Hierarchical Dispatching and Overriding

### 2017-10-11 NewVersion/sections/Overview.tex
Section 2

This is not the end of the story, because after the programmer defines \lstinline|DrawableSafeDeck|, he needs to override
\lstinline|Drawable.draw|, and give the implementation of drawing, so that the deck can indeed be visualized on the canvas.

\paragraph{Problem:} how to update the conflicting methods separately, after the triangle inheritance.

\paragraph{Potential fixes:} Unfortunately as far as we are concerned, the existing approaches are unsatisfactory.
One direction is to simply avoid this issue, by putting overriding before inheritance. For example, we define a new component
that extends \lstinline|Drawable|, simply draw the deck as a rectangle, and modifies the hierarchy:
\vspace{3pt}\begin{lstlisting}
interface DrawableRect extends Drawable {
  void draw() {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ....
  }
}

interface DrawableSafeDeck extends DrawableRect, SafeDeck {}
\end{lstlisting} \vspace{3pt}
This workaround seems to work, but there are severe issues:
\begin{itemize}
	\item It changes the hierarchy and existing code, hence breaks the modularity.
	\item The demand for separate overriding after the triangle inheritance comes especially when there is interaction. In the above code we assume
	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
	object, we have to either introduce field methods for delegation, or change the signature of \lstinline|draw| to take a parameter.
	Either way introduces unnecessary complexity and affects extensibility.
\end{itemize}
Another workaround in C++ adopts templates, but there are still issues and we put the discussion in Section~\ref{subsec:middleman}.

\paragraph{Our solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
\vspace{3pt}\begin{lstlisting}
interface DrawableSafeDeck extends Drawable, SafeDeck {
  void draw() override Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ...
  }
}

// main program
((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
\end{lstlisting}\vspace{3pt}
The direct support for individual overriding also works when there is interaction. In our formalization, this feature is necessary
and also involves in the algorithm of hierarchical dispatch.

\paragraph{Terminology:} The \lstinline|draw| methods we saw in previous subsections are called \textit{original methods} in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}. The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

\paragraph{Overview of hierarchical dispatching algorithm:} In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch. A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck|, it leads to ambiguity. The compiler is supposed to forbid the case.

>>>>

Method overriding is common in Object-Oriented Programming. 
With diamond inheritance where conflicting methods are intended to have 
the same semantics, method overriding is not a problem. If conflicting
methods arize from multiple parents, we can override all those methods 
in a single unified (or merged) method in the subclass. Therefore
further overriding is simple, because there is only one method that
can be overriden.

With unintentional method conflicts, however, the situation is more
complicated because different, separate, conflicting methods can exist
in a class. Ideally we would like to support overriding for those
methods too, in exactly the same way that overriding is available for 
other (non-conflicting) methods. However we need to be able to
override the individual conflicting methods, rather than overriding all
conflicting methods into a single merged method.  We illustrate the
problem and the need for a more refined overrding mechanism with 
an example.

Suppose that the programmer defines \lstinline|DrawableSafeDeck|, but he needs to override
\lstinline|Drawable.draw| and give a new implementation of drawing, so that the deck can indeed be visualized on the canvas.

%\paragraph{Problem:} how to update the conflicting methods separately, after the triangle inheritance.

\paragraph{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we known
(including C++), the existing approaches are unsatisfactory.
One direction is to simply avoid this issue, by putting overriding before inheritance. For example, we define a new component
that extends \lstinline|Drawable|, simply draw the deck as a rectangle, and modifies the hierarchy:
\vspace{3pt}\begin{lstlisting}
interface DrawableRect extends Drawable {
  void draw() {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ....
  }
}

interface DrawableSafeDeck extends DrawableRect, SafeDeck {}
\end{lstlisting} \vspace{3pt}
This workaround seems to work, but there are severe issues:
\begin{itemize}
	\item It changes the hierarchy and existing code, hence breaks the modularity.
	\item The demand for separate overriding after the triangle
          inheritance comes especially when there is
          interaction\bruno{what interaction?}. In the above code we assume
	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
	object, we have to either introduce field methods for delegation, or change the signature of \lstinline|draw| to take a parameter.
	Either way introduces unnecessary complexity and affects extensibility.
\end{itemize}

There are more involved workarounds in C++ using templates and complex
patterns, but such patterns are complex to use and there are still issues. A more detailed discussion of
such an approach is presented in Section~\ref{subsec:middleman}.

\paragraph{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
\vspace{3pt}\begin{lstlisting}
interface DrawableSafeDeck extends Drawable, SafeDeck {
  void draw() override Drawable {
    JFrame frame = new JFrame("Canvas");
    frame.setSize(600, 600);
    frame.getContentPane().setBackground(Color.red);
    frame.getContentPane().add(new Square(10,10,100,100));
    ...
  }
}

// main program
((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
\end{lstlisting}\vspace{3pt}\bruno{make override a keyword in
  lstlisting.}
Here the idea is that \emph{only} \lstinline{Drawable.draw} is
overriden. This is accomplished by specifying, in the method
definition, that only the method override only overrides the method 
from \lstinline|Drawable|.  
The direct support for individual overriding also works when there is interaction. In our formalization, this feature is necessary
and also involves in the algorithm of hierarchical dispatch.\bruno{the
last two sentences are a bit unclear. I think it is related to ``interaction''.}

\paragraph{Terminology:} The \lstinline|draw| methods we saw in
previous subsections\bruno{by now I saw many methods. Please be more precise.} are called \textit{original methods} in this paper, because they are originally defined in its interface.
In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}. The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.

\paragraph{Overview of hierarchical dispatching algorithm:} In our
model, triangle inheritance allows several original methods (branches)
to coexist, and hierarchical dispatch first finds the most specific
original method (branch), then it finds the most specific hierarchical
overriding on that branch. A quick counter-example is when there are
two hierarchical overriding methods on \lstinline|Drawable| in
\lstinline|DrawableSafeDeck|, it leads to ambiguity. The compiler is
supposed to forbid the case.\bruno{please show code illustrating this,
and improve explanation.}
